---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cehAforos

<!-- badges: start -->
<!-- badges: end -->

The goal of cehAforos is to allow users to easily download datasets for gauging stations in Spanish rivers.

## Installation

You can install the development version of cehAforos from [GitHub](https://github.com/) with:

```{r install_it}
# install.packages("pak")
pak::pak("emf-creaf/cehAforos")
```

## Example

This is a basic example which shows you how to download daily data from river gauging stations for the Ebro basin:

```{r example1}
library(cehAforos)
# Use verbose = TRUE (default) if you want to track progress.
x <- get_ceh_data(table = "afliq", basin = "ebro", verbose = FALSE)
```

<br>

We can retrieve as easily the same datasets for all stations and from all the basins by omitting the $\tt{basin}$ parameter.

```{r example2}
# x <- read_cedex_basin(table = "afliq", verbose = FALSE)
```

