---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


## Overview

<!-- badges: start -->
<!-- badges: end -->


The goal of the `hydrospain` R package is to allow users to easily download historical data from for gauging stations in Spanish rivers. Those datasets are available at the [CEDEX web](https://ceh.cedex.es/anuarioaforos/demarcaciones.asp) archive. Although files can be downloaded by hand one by one, `hydrospain` allows the automatic retrieval of any of those files, appending WGS84 UTM30 (EPSG:32630) coordinates to the datasets. In addition, date fields are formatted accordingly.


## Installation

You can install the development version of `hydrospain` from [GitHub](https://github.com/) with:

```{r install_it, eval = FALSE}
# install.packages("githubinstall")
# githubinstall::gh_install_packages("hydrospain", "devel")
library(hydrospain)
```


## Example

This is a basic example which shows you how to download daily data from river gauging stations for the Ebro basin:

```{r example1, eval = FALSE}
# Use verbose = TRUE (default) if you want to track progress.
x <- hydrospain(file_name = "afliq", basin_nam = "ebro", verbose = FALSE)
```

<br>

We can retrieve as easily the same file for all stations and from all the basins by omitting the $\tt{basin}$ parameter.

```{r example2, eval = FALSE}
x <- hydrospain(file_name = "afliq", verbose = FALSE)
```

<br>

Notice that the retrieval can be done for all basin stations at once, but files must be retrieved one by one. For a exhaustive list of files to download, go to the CEDEX web.
